### 2013-02-27 htdocs/colloid.tex
Additional comments on cholesteric BC
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig/trunk@1921 40876441-3496-0410-a613-a2fca35b2ae2

In three dimensions, the boundary condition Eq.~\ref{cholesteric_bc}
contains (potentially) 15 unknown derivatives
$\partial_\gamma Q_{\alpha\beta}$
corresponding to the 5 independent elements of the order parameter
tensor $Q_{xx}$, $Q_{xy}$, $Q_{xz}$, $Q_{yy}$, and $Q_{yz}$. At a
flat surface with, e.g., $n = (1, 0, 0)$, this is reduced to five unknown
gradients $\partial_x Q_{\alpha\beta}$ at the
boundary if we assume the tangential gradients $\partial_y Q_{\alpha\beta}$
and $\partial_z Q_{\alpha\beta}$ can be approximated
using the standard differencing method involving only fluid values of
$Q_{\alpha\beta}$. We proceed by
computing the constant terms
$$
- \kappa_1 q_0 n_\gamma (\epsilon_{\alpha\gamma\sigma} Q_{\sigma\beta}
+ \epsilon_{\beta\gamma\sigma}Q_{\sigma\alpha})
- w(Q_{\alpha\beta} - Q_{\alpha\beta}^0)
$$
using $Q_{\alpha\beta}$ from the adjacent fluid site, and an estimate
of $Q^0_{\alpha\beta}$ for the appropriate anchoring type. To these
constant terms are added the tangential gradients.
The gradients at the surface are then computed by solving a 5x5
linear algebra problem for $\partial_x Q_{\alpha\beta}$. This
allows the full gradient at the adjacent fluid site to be constructed.

@@

\begin{tabular}{|c|ccccc|}

\hline
&
$Q_{xx,x}$ & $Q_{xy,x}$ & $Q_{xz,x}$ & $Q_{yy,x}$ & $Q_{yz,x}$ \\
\hline
$Q_{xx}$ &
$\kappa_0 n_x$ & $-\kappa_1 n_y$ & $-\kappa_1 n_z$ & & \\
$Q_{xy}$ &
$\kappa_0 n_y$ & $\kappa' n_x$ & & $-\kappa_1 n_y$  & $-\kappa_1 n_z$  \\
$Q_{xz}$ &
$\kappa' n_z$ & & $\kappa' n_x$ & $\kappa_1 n_z$ & $-\kappa_1 n_y$ \\
$Q_{yy}$ &
 & $\kappa_0 n_y$ & & $\kappa_1 n_x$ & \\
$Q_{yz}$ &
 & $\kappa_0 n_z$ & $\kappa_0 n_y$ & & $2\kappa_1 n_x$ \\
\hline
\hline
&
$Q_{xx,y}$ & $Q_{xy,y}$ & $Q_{xz,y}$ & $Q_{yy,y}$ & $Q_{yz,y}$ \\
\hline
$Q_{xx}$ &
$\kappa_1 n_y$ & $\kappa_0 n_x$ & & & \\
$Q_{xy}$ &
$-\kappa_1 n_x$ & $\kappa' n_y$ & $-\kappa_1 n_z$ & $\kappa_0 n_x$ & \\
$Q_{xz}$ &
 & $\kappa_0 n_z$ & $2\kappa_1 n_y$ & & $\kappa_0 n_x$ \\
$Q_{yy}$ &
 & $-\kappa_1 n_x$ & & $\kappa_0 n_y$ & $-\kappa_1 n_z$\\
$Q_{yz}$ &
$\kappa_1 n_z$ & & $-\kappa_1 n_x$ & $\kappa' n_z$ & $\kappa' n_y$\\
\hline
\hline
&
$Q_{xx,z}$ & $Q_{xy,z}$ & $Q_{xz,z}$ & $Q_{yy,z}$ & $Q_{yz,z}$ \\
\hline
$Q_{xx}$ &
$\kappa_1 n_z$ & & $\kappa_0 n_x$ & & \\
$Q_{xy}$ &
 & $2\kappa_1 n_z$ & $\kappa_0 n_y$ & & $\kappa_0 n_x$ \\
$Q_{xz}$ &
$-\kappa' n_x$ & $-\kappa_1 n_y$ & $\kappa' n_z$ & $-\kappa_0 n_x$ & \\
$Q_{yy}$ &
 & & & $\kappa_1 n_z$ & $\kappa_0 n_y$  \\
$Q_{yz}$ &
$-\kappa_0 n_y$ & $-\kappa_1 n_x$ & & $-\kappa' n_y$ & $\kappa' n_z$ \\
\hline
\end{tabular}
\end{center}
\caption{Coefficients of the various derivatives of the order parameter
tensor appearing in five equations for the independent elements of the
order parameter. Note $\kappa_0 + \kappa_1 = \kappa'$ and all the
coefficients have been multiplied by a factor of 2.}
\label{tab:cholesteric_bcs}
\end{table} 
}

>>>>

In three dimensions, the boundary condition Eq.~\ref{cholesteric_bc}
provides six equations containing (potentially) 18 unknown derivatives
$\partial_\gamma Q_{\alpha\beta}$
corresponding to the 6 independent elements of the order parameter
tensor $Q_{xx}$, $Q_{xy}$, $Q_{xz}$, $Q_{yy}$, $Q_{yz}$, $Q_{zz}$.
Note that the equation corresponding to $Q_{zz}$ must appear to
retain isotropy. However, $Q_{zz}$ itself, and its derivatives,
 may be replaced via the
constraint on the trace of $Q_{\alpha\beta}$. We can therefore either
solve a fully determined system including $Q_{zz}$, and then impose
tracelessness on the result, or replace $Q_{zz}$ and solve six
equations for five unknowns, with the sixth equation acting as the
constraint. These methods provide the same answer for cases where
the surface normal is along the coordinate directions.

At a flat surface with, e.g., $n = (1, 0, 0)$, the number of unknowns
are the gradients $\partial_x Q_{\alpha\beta}$ at the
boundary if we assume the tangential gradients $\partial_y Q_{\alpha\beta}$
and $\partial_z Q_{\alpha\beta}$ can be approximated
using the standard differencing method involving only fluid values of
$Q_{\alpha\beta}$. We proceed by
computing the constant terms
$$
- \kappa_1 q_0 n_\gamma (\epsilon_{\alpha\gamma\sigma} Q_{\sigma\beta}
+ \epsilon_{\beta\gamma\sigma}Q_{\sigma\alpha})
- w(Q_{\alpha\beta} - Q_{\alpha\beta}^0)
$$
using $Q_{\alpha\beta}$ from the adjacent fluid site, and an estimate
of $Q^0_{\alpha\beta}$ for the appropriate anchoring type. To these
constant terms are added the tangential gradients.
The gradients at the surface are then computed by solving a 5x5
linear algebra problem for $\partial_x Q_{\alpha\beta}$. This
allows the full gradient at the adjacent fluid site to be constructed.

@@

\begin{tabular}{|c|cccccc|}

\hline
&
$Q_{xx,x}$ & $Q_{xy,x}$ & $Q_{xz,x}$ & $Q_{yy,x}$ & $Q_{yz,x}$ & $Q_{zz,x}$\\
\hline
$Q_{xx}$ &
$\kappa_0 n_x$ & $-\kappa_1 n_y$ & $-\kappa_1 n_z$ & & &\\
$Q_{xy}$ &
$\kappa_0 n_y$ & $\kappa' n_x$ & & $-\kappa_1 n_y$  & $-\kappa_1 n_z$ & \\
$Q_{xz}$ &
$\kappa_0 n_z$ & & $\kappa' n_x$ & & $-\kappa_1 n_y$ &$ -\kappa_1 n_z$\\
$Q_{yy}$ &
 & $\kappa_0 n_y$ & & $\kappa_1 n_x$ & &\\
$Q_{yz}$ &
 & $\kappa_0 n_z$ & $\kappa_0 n_y$ & & $2\kappa_1 n_x$ & \\
$Q_{zz}$ &
 & & $\kappa_0 n_z$ & & & $\kappa_1 n_x$\\
\hline
\hline
&
$Q_{xx,y}$ & $Q_{xy,y}$ & $Q_{xz,y}$ & $Q_{yy,y}$ & $Q_{yz,y}$ & $Q_{zz,y}$\\
\hline
$Q_{xx}$ &
$\kappa_1 n_y$ & $\kappa_0 n_x$ & & & &\\
$Q_{xy}$ &
$-\kappa_1 n_x$ & $\kappa' n_y$ & $-\kappa_1 n_z$ & $\kappa_0 n_x$ & &\\
$Q_{xz}$ &
 & $\kappa_0 n_z$ & $2\kappa_1 n_y$ & & $\kappa_0 n_x$ & \\
$Q_{yy}$ &
 & $-\kappa_1 n_x$ & & $\kappa_0 n_y$ & $-\kappa_1 n_z$ & \\
$Q_{yz}$ &
 & & $-\kappa_1 n_x$ & $\kappa_0 n_z$ & $\kappa' n_y$ & $-\kappa_1 n_z$\\
$Q_{zz}$ &
 & & & & $\kappa_0 n_z$ & $\kappa_1 n_y$\\
\hline
\hline
&
$Q_{xx,z}$ & $Q_{xy,z}$ & $Q_{xz,z}$ & $Q_{yy,z}$ & $Q_{yz,z}$ & $Q_{zz,z}$\\
\hline
$Q_{xx}$ &
$\kappa_1 n_z$ & & $\kappa_0 n_x$ & & & \\
$Q_{xy}$ &
 & $2\kappa_1 n_z$ & $\kappa_0 n_y$ & & $\kappa_0 n_x$ & \\
$Q_{xz}$ &
$-\kappa_1 n_x$ & $-\kappa_1 n_y$ & $\kappa' n_z$ & & & $\kappa_0 n_x$  \\
$Q_{yy}$ &
 & & & $\kappa_1 n_z$ & $\kappa_0 n_y$ & \\
$Q_{yz}$ &
 & $-\kappa_1 n_x$ & & $-\kappa_1 n_y$ & $\kappa' n_z$ & $\kappa_0 n_y$ \\
$Q_{zz}$ &
 & & $-\kappa_1 n_x$ & & $-\kappa_1 n_y $ & $\kappa_0 n_z$\\
\hline
\end{tabular}
\end{center}
\caption{Coefficients of the various derivatives of the order parameter
tensor appearing in six equations for the elements of the
order parameter (including $Q_{zz}$).
Note $\kappa_0 + \kappa_1 = \kappa'$ and all the
coefficients have been multiplied by a factor of 2 in the off-diagonal
equations.}
\label{tab:cholesteric_bcs}
\end{table} 
}
